Value-Suppressing Uncertainty Maps

### 2017-03-31 paper/template.tex
Fix paper
prep for merge.

\newcommand{\figref}[1]{\hyperref[#1]{Figure~\ref*{#1}}}

\newcommand{\ie}{{i.e.}\xspace}
\newcommand{\eg}{{e.g.,}\xspace}
\newcommand{\cf}{{c.f.}\xspace}
\newcommand{\ea}{{et~al.}\xspace}
\newcommand{\aka}{{a.k.a.}\xspace}
\newcommand{\etc}{{etc.}\xspace}

@@

For each task, participants saw one of three types of thematic maps. Either two \textbf{juxtaposed} maps side-by-side, with separate encodings for value and uncertainty, a traditional \textbf{bivariate} map, where value and uncertainty are orthogonally encoded, or a \textbf{VSUM}. Figure \ref{fig:stimuli} shows examples of these factor levels. Other factors included the size of the map (either a 4x4 or 8x8 grid), and (for the prediction task), the question framing (attack or defense). These secondary factors were evenly blocked across stimuli. Fatigue effects were significant in piloting, and so we limited the number of replicates: participants saw 18 stimuli (6 for each map type) for the identification task, and 12 (4 for each map type) for the prediction task.

@@

We limited our population to Turkers from the United States, with a prior task approval rate of at least 90\%. As the experimental tasks required multi-hue color perception, we presented participants with a set of Ishihara plates as a pretest, and excluded participants who either misidentified the values in the plates, or who self-reported as having a color vision deficiency (CVD) in the post-test. Based on piloting, we paid participants \$2 dollars an hour, for a target rate of \$8/hour. After completion of the main tasks, we solicited demographic information, and performed a domain-agnostic general risk aversion assay~\cite{mandrik2005exploring}.

\section{Discussion}
\subsection{Limitations and Future Work}
% When should you use these things?

\section{Conclusion}

>>>>

\newcommand{\figref}[1]{\hyperref[#1]{Figure~\ref*{#1}}}
\usepackage{xspace}
\newcommand{\ie}{{i.e.}\xspace}
\newcommand{\eg}{{e.g.,}\xspace}
\newcommand{\cf}{{c.f.}\xspace}
\newcommand{\ea}{{et~al.}\xspace}
\newcommand{\aka}{{a.k.a.}\xspace}
\newcommand{\etc}{{etc.}\xspace}

@@

For each task, participants saw one of three types of thematic maps. Either two \textbf{juxtaposed} maps side-by-side, with separate encodings for value and uncertainty, a traditional \textbf{bivariate} map, where value and uncertainty are orthogonally encoded, or a \textbf{VSUM}. Figure \ref{fig:conditions} shows examples of these factor levels. Other factors included the size of the map (either a 4x4 or 8x8 grid), and (for the prediction task), the question framing (attack or defense). These secondary factors were evenly blocked across stimuli. Fatigue effects were significant in piloting, and so we limited the number of replicates: participants saw 18 stimuli (6 for each map type) for the identification task, and 12 (4 for each map type) for the prediction task.

@@

We limited our population to Turkers from the United States, with a prior task approval rate of at least 90\%. As the experimental tasks required multi-hue color perception, we presented participants with a set of Ishihara plates as a pretest, and excluded participants who either misidentified the values in the plates, or who self-reported as having a color vision deficiency (CVD) in the post-test. Based on piloting, we paid participants \$2 dollars an hour, for a target rate of \$8/hour. After completion of the main tasks, we solicited demographic information. We recruited a total of 24 participants for this experiment: 4 female, 19 male, and 1 who declined to state ($M_{\text{age}}$= 32, $SD_{\text{age}}$ = 7.5). All reported having either college degrees, or some college experience. Average self-reported experience with interpreting graphs and charts was low (1.9 on a 5 point Likert scale, with 1 indicating ``No experience''), and no participant reported experience greater than 3 out of 5.

\section{Discussion}

\subsection{Limitations and Future Work}
% When should you use these things?

\subsection{Conclusion}
